Diverse Genotype-by-Weather Interactions in Switchgrass

### 2024-08-18 manuscript/revision2/SI_Appendix/SI_Appendix.qmd
revision2: Edit author middle initial in SI Appendix

---
title: Diverse Genotype-by-Weather Interactions in Switchgrass
pdf-engine: pdflatex
format:
  pnas-si-pdf:
    keep-tex: false  
author:
  - name: Alice H. MacQueen
    affiliations:
      - name: University of Texas at Austin
        id: a
        department: Department of Integrative Biology
        city: Austin
        state: TX
        postal-code: 78712
    email: alicem@uchicago.edu
    attributes:
      equal-contributor: true
      corresponding: true
  - name: Li Zhang
    affiliations:
      - ref: a
    attributes:
      equal-contributor: true
  - name: Samuel A. Smith
    affiliations:
        - ref: a
    attributes:
      equal-contributor: true
  - name: Jason Bonnette
    affiliations:
          - ref: a
  - name: Arvid R. Boe
    affiliations:
      - name: South Dakota State University
        id: b
        department: Department of Agronomy
        city: Brookings
        state: SD
        postal-code: 57006
  - name: Phillip A. Fay
    affiliations:
      - name: USDA-ARS
        id: c
        department: Grassland, Soil and Water Research Laboratory
        city: Temple
        state: TX
        postal-code: 76502
  - name: Felix B. Fritschi
    affiliations:
      - name: University of Missouri
        id: d
        department: Division of Plant Sciences
        city: Columbia
        state: MO
        postal-code: 65211
  - name: David B. Lowry
    affiliations:
      - name: Michigan State University
        id: e
        department: Department of Plant Biology
        city: East Lansing
        state: MI
        postal-code: 48824
  - name: Robert B. Mitchell
    affiliations:
      - name: USDA-ARS
        id: f
        department: Wheat, Sorghum, and Forage Research Unit
        city: Lincoln
        state: NE
        postal-code: 68583
  - name: Francis M. Rouquette Jr
    affiliations:
      - name: Texas A&M University
        id: g
        department: Texas A&M AgriLife Research and Extension Center
        city: Overton
        state: TX
        postal-code: 75684
  - name: Yanqi Wu
    affiliations:
      - name: Oklahoma State University
        id: h
        department: Department of Plant and Soil Sciences
        city: Stillwater
        state: OK
        postal-code: 74078
  - name: Arbel Harpak
    affiliations:
      - ref: a
  - name: Thomas E. Juenger
    affiliations:
      - ref: a
    attributes:
      corresponding: true
    email: tjuenger@utexas.edu
bibliography: bibliography.bib  
fontsize: "9pt"
classoption:
 - twoside
---

>>>>

---
title: Diverse Genotype-by-Weather Interactions in Switchgrass
pdf-engine: pdflatex
format:
  pnas-si-pdf:
    keep-tex: false  
author:
  - name: Alice H. MacQueen
    affiliations:
      - name: University of Texas at Austin
        id: a
        department: Department of Integrative Biology
        city: Austin
        state: TX
        postal-code: 78712
    email: alicem@uchicago.edu
    attributes:
      equal-contributor: true
      corresponding: true
  - name: Li Zhang
    affiliations:
      - ref: a
    attributes:
      equal-contributor: true
  - name: Samuel P. Smith
    affiliations:
        - ref: a
    attributes:
      equal-contributor: true
  - name: Jason E. Bonnette
    affiliations:
          - ref: a
  - name: Arvid R. Boe
    affiliations:
      - name: South Dakota State University
        id: b
        department: Department of Agronomy
        city: Brookings
        state: SD
        postal-code: 57006
  - name: Philip A. Fay
    affiliations:
      - name: USDA-ARS
        id: c
        department: Grassland, Soil and Water Research Laboratory
        city: Temple
        state: TX
        postal-code: 76502
  - name: Felix B. Fritschi
    affiliations:
      - name: University of Missouri
        id: d
        department: Division of Plant Sciences
        city: Columbia
        state: MO
        postal-code: 65211
  - name: David B. Lowry
    affiliations:
      - name: Michigan State University
        id: e
        department: Department of Plant Biology
        city: East Lansing
        state: MI
        postal-code: 48824
  - name: Robert B. Mitchell
    affiliations:
      - name: USDA-ARS
        id: f
        department: Wheat, Sorghum, and Forage Research Unit
        city: Lincoln
        state: NE
        postal-code: 68583
  - name: Francis M. Rouquette Jr
    affiliations:
      - name: Texas A&M University
        id: g
        department: Texas A&M AgriLife Research and Extension Center
        city: Overton
        state: TX
        postal-code: 75684
  - name: Yanqi Wu
    affiliations:
      - name: Oklahoma State University
        id: h
        department: Department of Plant and Soil Sciences
        city: Stillwater
        state: OK
        postal-code: 74078
  - name: Arbel Harpak
    affiliations:
      - ref: a
  - name: Thomas E. Juenger
    affiliations:
      - ref: a
    attributes:
      corresponding: true
    email: tjuenger@utexas.edu
bibliography: bibliography.bib  
fontsize: "9pt"
classoption:
 - twoside
---
